%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Robin Tinashe Mukanganise} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Flat 2, 2 Marston Ferry Road} % Your address
\moveleft.5\hoffset\centerline{Oxford, OX2 7EE}
\moveleft.5\hoffset\centerline{United Kingdom}
\moveleft.5\hoffset\centerline{+44 7521081560}
\moveleft.5\hoffset\centerline{seechrobin@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl BSc. Computer Science,}  \hfill December 2013 \\
University of Cape Town, Cape Town, South Africa\\
 

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNOLOGY \\ SKILLS} 

{\sl Programming Languages:} Java, Python, Objective-C, Swift, JavaScript, PHP. \\
{\sl Web Backend Technologies:}  NodeJS,Laravel, MongoDB, ElasticSearch, PostgreSQL, MySQL, SQLite. \\
{\sl Web Frontend Technologies:} AngularJS, JQuery, Ionic, PhoneGap, Laravel, Bootstrap, Less, CSS, HTML. \\
{\sl Software Engineering:} Agile, Continuous Integration, Scrum, Version control, Requirements analysis. \\
{\sl Software Tools:} Atlassian Suite, Jenkins, Git, Gulp, NPM, Bower, Xcode, Joomla. \\
{\sl Platforms:} MacOS, iOS, Linux, Windows. \\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}

{\sl App and Web Developer} \hfill January 2016 - Present \\
University of Oxford, Oxford, United Kingdom
\vspace{5mm} %5mm vertical space
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Responsible for the development, implementation and review of websites and web technologies to support teaching and research activities, working with academic and administrative stakeholders to ensure that sites meet defined needs and are delivered to schedule and to cost.
\item Creation, maintenance and updating of site content in accordance with legislation, University policy and acknowledged industry best-practice.
\item Work with the MRB IT team (Internal IT Team) to ensure the continued provision of web hosting services ensuring that the current web platform is maintained and secure
\item Day to day administration of Microsoft Internet Information Services,PHP and MySQL.
\item Respond to queries regarding web project start-ups, liaise with suppliers and contractors and advise on University policies and procedures as appropriate.
\item Provide training and user documentation new systems.
\item Handle departmental queries as part of the team-based approach to user support, we support Politics, Sociology and Economics departments.
\item Doing initial research on implementing iBeacons technology in the Manor Road Building at Oxford University.
\item Creating features that enhance the current systems and removing old legacy code.
\item Designed and developed a Tutorial Management System in AngularJS, PHP Laravel and MySQL.

\end{itemize} 

\vspace{39 mm}
{\sl iOS Developer} \hfill September 2015 - December 2015 \\
wiGroup, Cape Town, South Africa
\vspace{5mm} %5mm vertical space
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Maintained and enhanced a suite of about 10 apps that frequently ranked in the top 10 of the South African App store. 
\item Created a caching mechanisms for 2 apps that where responsible for up to a millions API calls in a month.
\item Migrated and re-factored legacy code from Objective-C to Swift
\item Implemented new layout and new user interfaces.
\item Creating and maintaining Jenkins build server for continuous integration.
\item Deploying applications on request to assist the sales team.
\item Developed and deployed standardized techniques for the codebase.
\item Made sure that the applications were in line with standard security policies to protect sensitive data.
\item Deploying apps to the App store and fixing submission related issue from the App store.
\end{itemize}

 {\sl Chief Technology Officer} \hfill November 2014 - January 2017 \\
Daub, Harare, Zimbabwe
\vspace{5mm} %5mm vertical space
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Leading the technology side of the business
\item Leading the Software Engineering effort to building an animated meme social network app in Objective-C
\item Involved in doing all the Quality Assurance, and covering all aspects of the whole SDLC
\item Advocating the app to potential partners and investors
\item Employing the lean start-up strategy to build the company.
\item Preparing the app for submission to the App Store, liaising with designers, marketing and the CEO to make sure that schedule was adhered to and met.
\end{itemize}
 
 
{\sl Software Developer} \hfill December 2012 - August 2015\\
Grapevine Interactive, Cape Town, South Africa
\vspace{5mm} %5mm vertical space
\begin{itemize} \itemsep -2pt % Reduce space between items 
\item I was responsible for building world class technology in Java, Python and Objective-C
\item Creating documentation for new software
\item Deploying apps to Appstore and for ad-hoc distribution 
\item Implemented a new testing strategy for business analysts and developers
\item Troubleshooting/trouble forecasting bugs as per bug report from the product manager
\item Training team members Python programming
\end{itemize}

 {\sl Co-Founder and Software Developer} \hfill December 2010 - December 2014\\
Seech.Inc, Cape Town, South Africa
\vspace{5mm} %5mm vertical space
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed an android application called Postee
\item Building interactive website in HTML and JavaScript
\item Doing IT maintenance, fixing and building computers
\end{itemize} 



 
%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{Interests} 
Surfing, Golf, Cycling \\




 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}